gratia: An R package for exploring generalized additive models

### 2025-06-21 README.Rmd
wrong links on r-universe badges

[![r-universe version](https://r-lib.r-universe.dev/gratia/badges/version)](https://r-lib.r-universe.dev/gratia)
[![r-universe status](https://r-lib.r-universe.dev/gratia/badges/checks)](https://r-lib.r-universe.dev/gratia)
<!-- badges: end -->

>>>>

[![r-universe version](https://gavinsimpson.r-universe.dev/gratia/badges/version)](https://gavinsimpson.r-universe.dev/gratia)
[![r-universe status](https://gavinsimpson.r-universe.dev/gratia/badges/checks)](https://gavinsimpson.r-universe.dev/gratia)
<!-- badges: end -->
